Microplatforms: Product platforms as code

### 2018-03-14 paper.tex
more biblio

\begin{figure}[b]
	\setlength{\fboxsep}{1em}
	\fbox{
		\begin{minipage}{0.43\textwidth}\raggedright
			Service name, Programming language(s), Programming paradigm(s), Architectural choices, Integration pattern(s), Transport protocols, Authentication, Authorization, Reporting, ETLs, Databases, Caching, Platform libraries, Service dependencies, CI Pipeline dependencies, 3rd party library dependencies, 3rd party service dependencies, Security threat model, License audit, Compliance audit, Capacity plan, Provisioning plan, Cost reporting plan, Monitoring plan, Maintenance process, Backup and Restore process, Secret management, Secret rotation, On-Call schedule, Configuration management, Workflow management, Alerts, Log aggregation, Unhandled failure aggregation, Operations and incident response runbooks, API documentation, Source Code Repository, Humane Service Registry, Service Discovery Registry, Distributed Tracing Registry, Monitoring Dashboard Registry, Build Artifact Repository, CI pipeline(s): Build, Test, Publish, Integration tests, Contract tests, Canary, Deploy, Post deploy tests.
		\end{minipage}
	}
	\caption{48 concerns for a single microservice~\cite{Treadway17}}
	\label{fig:concerns}
\end{figure}

@@

An important consideration for a product platform is the cost of building it and the ongoing maintenance involved, including infrastructure provisioning, maintenance (security patches) and scaling capacity to support the products that need to run on it. The effort involved should not be under-estimated~\cite{saaspdf24:online} and is the motivation behind most digital product now running on cloud infrastructure. We will discuss the reasons for this cost reduction in more detail in sections \ref{sec:cost} and \ref{sec:automation}.

@@

In Fig 1 we show 48 cross-cutting concerns, identified by Sean Treadway [], that need addressing for each microservice. None of them are directly related to adding customer value. With microservices architecture, we have made a rod for our own back: developers should be able to write code that directly adds customer value and they should not need to worry about any of the concerns listed. These can be addressed by employing a service mesh (such as Istio []). It allows us to declaratively specify \textbf{policy as code} providing services such as intelligent routing and load balancing, traffic shaping and shifting, security policies, ingress and egress rules, circuit breaking [] and upstream call retries, rate limits, call tracing, telemetry and reporting. It is even possible to use a service mesh to inject faults into the system to test reliability features that may have been overlooked. All of this configuration is declarative and stored as code alongside the orchestration configuration.

@@

\bibliography{bibliography}
\bibliographystyle{apalike}

>>>>

\begin{figure}[b]
	\setlength{\fboxsep}{1em}
	\fbox{
		\begin{minipage}{0.43\textwidth}\raggedright
			Service name, Programming language(s), Programming paradigm(s), Architectural choices, Integration pattern(s), Transport protocols, Authentication, Authorization, Reporting, ETLs, Databases, Caching, Platform libraries, Service dependencies, CI Pipeline dependencies, 3rd party library dependencies, 3rd party service dependencies, Security threat model, License audit, Compliance audit, Capacity plan, Provisioning plan, Cost reporting plan, Monitoring plan, Maintenance process, Backup and Restore process, Secret management, Secret rotation, On-Call schedule, Configuration management, Workflow management, Alerts, Log aggregation, Unhandled failure aggregation, Operations and incident response runbooks, API documentation, Source Code Repository, Humane Service Registry, Service Discovery Registry, Distributed Tracing Registry, Monitoring Dashboard Registry, Build Artifact Repository, CI pipeline(s): Build, Test, Publish, Integration tests, Contract tests, Canary, Deploy, Post deploy tests.
		\end{minipage}
	}
	\caption{48 concerns for a single microservice~\cite{Treadway17:online}}
	\label{fig:concerns}
\end{figure}

@@

An important consideration for a product platform is the cost of building it and the ongoing maintenance involved, including infrastructure provisioning, maintenance (security patches) and scaling capacity to support the products that need to run on it. The effort involved should not be under-estimated~\cite{saaspdf24:online} and is the motivation behind most digital product now running on cloud infrastructure. We will discuss the reasons for this cost reduction in more detail in sections~\ref{sec:cost} and~\ref{sec:automation}.

@@

In Fig 1 we show 48 cross-cutting concerns, identified by Sean Treadway~\cite{Treadway17:online}, that need addressing for each microservice. None of them are directly related to adding customer value. With microservices architecture, we have made a rod for our own back: developers should be able to write code that directly adds customer value and they should not need to worry about any of the concerns listed. These can be addressed by employing a service mesh (such as Istio []). It allows us to declaratively specify \textbf{policy as code} providing services such as intelligent routing and load balancing, traffic shaping and shifting, security policies, ingress and egress rules, circuit breaking [] and upstream call retries, rate limits, call tracing, telemetry and reporting. It is even possible to use a service mesh to inject faults into the system to test reliability features that may have been overlooked. All of this configuration is declarative and stored as code alongside the orchestration configuration.

@@

\bibliography{bibliography}
\bibliographystyle{plain}
